### 2020-02-17 Common/chapters/medical.tex
Julien and Johan: typos, remake screenshots and minors
Julien and Johan: tools to convert medical files to PNG

\subsection{DICOM file format}

@@

\section{Conversion}

@@

>>>>

\subsection{DICOM file format}
\label{sec:DICOM}

@@

@@

\section{Conversion to PNG}

In addition to the visualization tools, libraries allowing to convert medical files into PNG files were developped. The main one is called "anydatasettopng" and is the one to use to convert any file format to PNG since it makes use of the others. Given a root directory, it scans the latter and its subdirectories to find all DICOM, NIfTI and RAW/MHD files. Then, each file is converted to PNG and saved into the same directory as the one it came from. This library allows to keep an easily accessible visual representation of medical files without having to rely on a specific piece of software to display them. Finally, it also played the role of debugging tool since the conversion techniques are the same as the ones used further in this work.

\subsection{8-bit conversion}
